---
title: "Exercise 1"
output: github_document
---

```{r setup, include=TRUE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r eval=TRUE}
library(dplyr)
```


```{r eval=TRUE}
library(tidygraph)
```


```{r eval=TRUE}
library(tidyverse)
```

```{r eval=TRUE}
library(ggraph)
```

```{r eval=TRUE}
library(igraph)
```

```{r eval=TRUE}
Data <- read.csv('/Users/Brock/Desktop/Exercise1.csv')

```

```{r eval=TRUE}
FGraph = graph_from_data_frame(d=Data,vertices=NULL ,directed=FALSE)
FGraph
```

```{r eval=TRUE}
degree(FGraph, v=V(FGraph))
```

```{r eval=TRUE}
betweenness(FGraph)
```

```{r eval=TRUE}
evcent(FGraph)$vector
```

```{r eval=TRUE}
ggraph(FGraph) +
  geom_edge_link() +
  geom_node_point()
```

Using the above graph and the calculated measures, there are various insights.
Seats B, C and D have degrees of 5 in centrality. This would provide the opportunity to connect with more people sitting nearby.
In betweeness, B scores the highest, with C trailing slightly. D scores lower in this metric.
D scores the highest in the eigenvector metric, slightly ahead of B and C.
Considering the results above, B appears to be a promising option.
